TGI-spinal-power

### 2022-05-09 analysis/tgispine_lme_power.Rmd
preparing data for beta regression

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)

@@

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)
```
Need to change this and create two cold models - one with zero inflated and one without
Also need to check Bayesian
- Check out Jesper's code

# Getting data frame and paths
```{r}
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/'
setwd(datPath)

df_phs <- read.csv(file.choose())

# need to recode levels for cold_probe to reduce number of levels from 4 to 2
df_phs$cold_location[df_phs$cold_probe == 'distal'] <- 'dist_rostr' 
df_phs$cold_location[df_phs$cold_probe == 'rostral'] <- 'dist_rostr'
df_phs$cold_location[df_phs$cold_probe == 'proximal'] <- 'prox_caud'
df_phs$cold_location[df_phs$cold_probe == 'caudal'] <- 'prox_caud'
df_phs$cold_location <- as.factor(df_phs$cold_location)
```

Create the first model. There is one model for each rating (instead of using rating as a parameter in the model).
First, going to try this on a very simple model where effect of manipulation (TGI vs. control) will be tested on rating of cold thermode, with subject as random effect
```{r}
# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_phs$cold <- df_phs$VAScold/100
df_phs$warm <- df_phs$VASwarm/100
df_phs$burn <- df_phs$VASburning/100
df_phs$ID <- factor(df_phs$ID)

# Summarise data per rating, per participant
sum_burn <- aggregate(burn~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_warm <- aggregate(warm~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
sum_cold <- aggregate(cold~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
# then compile all data again
sum_burn$VAS = 'burn'
names(sum_burn)[6] <- 'rating'
sum_warm$VAS = 'warm'
names(sum_warm)[6] <- 'rating'
sum_cold$VAS = 'cold'
names(sum_cold)[6] <- 'rating'
df_sum <- rbind(sum_cold, sum_warm)
df_sum <- rbind(df_sum, sum_burn)
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(rating ~ manipulation + condition + cold_location + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_phs$warm)
# then model warm VAS
```
# Look at model assumptions
```{r}
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)

@@

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)

# setting working directory
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
knitr::opts_knit$set(root.dir = datPath)
```

# Getting data and reformatting to fit model
```{r}
df <- read.csv('STGI_compiled-data.csv')

# need to recode levels for cold_probe to reduce number of levels from 4 to 2
df$cold_location[df$cold_probe == 'distal'] <- 'dist_rostr' 
df$cold_location[df$cold_probe == 'rostral'] <- 'dist_rostr'
df$cold_location[df$cold_probe == 'proximal'] <- 'prox_caud'
df$cold_location[df$cold_probe == 'caudal'] <- 'prox_caud'
df$cold_location <- as.factor(df$cold_location)

# reshape data so that there is one rating column per participant, with a VAS column = type of rating
df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburning"), 
                        id.vars=c("ID","trial_n","manipulation","procedure",
                                  "trial_type","arm","condition","cold_location"),
             variable.name = 'VAS', value.name = 'rating')
# rename the VAS ratings
df_VAS <- df_VAS %>% 
  mutate(VAS = revalue(VAS, c("VAScold" = "cold",
                                    "VASwarm" = "warm",
                                    "VASburning" = "burning")))

# to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$beta-0.0001, df_VAS$beta <- df_VAS$rating)

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_VAS$beta <- df_VAS$beta/100
df_VAS$ID <- factor(df_VAS$ID)

# Summarise data per rating, per participant
df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
                    median, data = df)
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(cold ~ manipulation + condition + cold_location + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df)
summary(model.cold)
# then model warm VAS
```
# Look at model assumptions
```{r}
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```
